Convex Surrogates via Polyhedral Losses

### 2019-02-02 cvx-fin.tex
sec 2

\begin{definition}[Calibrated Link]\label{def:links}
  Let properties $\gamma:\simplex\toto\R$ and $\Gamma:\simplex\toto\R'$ be given.
  A \emph{link function} is a map $\psi:\R'\to\R$.
  We say that a link $\psi$ is:
  \begin{itemize}
  \item \emph{Calibrated} if for all $p\in\simplex$, $r'\in \Gamma(p) \implies \psi(r') \in \gamma(p)$; in other words, if for all $r'\in\R'$, $\Gamma_{r'} \subseteq \gamma_{\psi(r')}$;
  \item \emph{Separated}, with respect to a loss $L$ eliciting $\Gamma$, if for all $p \in \simplex$,
  \begin{align*}
  \inf_{u \in \R'; \psi(u) \not \in \gamma(p)} \E_{Y\sim p}[L(u, Y)] > \inf_{u \in \R'}\E_{Y\sim p}[L(u, Y)]~.
  \end{align*}
  \end{itemize}
\end{definition}

Roughly speaking, a calibrated link requires that optimal surrogate reports map to optimal original reports, while a separated link adds the stronger guarantee that one cannot approach the optimal surrogate loss while making suboptimal original predictions.
A classic example of a link which is both calibrated and separated is $\psi = \sgn$ when $\gamma=\mode$ and $L$ is either hinge loss or logistic loss.
On the other hand, the link $\psi(u) =
\begin{cases}
  -1 & u \leq -1\\
  1 & u > -1
\end{cases}$
would not be separated for hinge loss, but it would still be calibrated, as the reports $u\in(-1,1)$ are optimal for hinge loss only when $p=(1/2,1/2)$, in which case both $-1$ and $1$ are optimal for the mode (0-1 loss).
\raft{Aside about other link definitions commented out}
% As a brief aside, it is interesting to contrast the definitions above with the following: a link is
% \emph{exhaustive} if for all $p\in\simplex$, $\gamma(p) = \psi(\Gamma(p)) := \{\psi(r') : r'\in\Gamma(p)\}$.
% A \emph{strong link} is a set-valued function $\psi:\R'\toto\R$ such that for all $p\in\simplex$ and $r'\in\R'$, we have $r'\in\Gamma(p) \implies \gamma(p) = \psi(r')$.
% If sign is interpreted as set-valued (0 maps to $\{1,-1\}$, then it is strong for logistic.  If not, sign is not exhaustive for logistic.  Sign is exhaustive for hinge.}

@@

Often one is given a property $\gamma$ (typically via a discrete loss $\ell$) and one seeks a surrogate loss $L$ with certain attributes, such as convexity, smoothness, etc.
In doing so, we may be interested in the minimum number of dimensions needed for such an indirect elicitation scheme; this is the notion of \emph{elicitation complexity}~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
The two notions of elicitation complexity we use most are as follows: let $\eliccvx(\gamma)$ be the minimum dimension $d$ such that $\gamma$ can be indirectly elicited by a convex loss function $L: \R'^d \to \reals^\Y_+$, and $\elicpoly(\gamma)$ the minimum such $d$ where $L$ is polyhedral.
We will also discuss $\eliccts$, which is the complexity with respect to continuous, real-valued, non-locally-constant properties (\S~\ref{sec:1d}), and $\elicembed$, which is the minimum dimension for $\gamma$ to be embedded (Definition~\ref{def:embedding-dim}).

@@

  A property of interest similar to the mode is the $\abstain{\alpha}$ property.
  In this property in which one reports the most likely outcome if the probability of such an outcome is greater than $1-\alpha$, and otherwise ``abstains'' from reporting.
  That is, $\gamma(p) = \argmax_{r \in \R}p_r$ if $\max_{r \in \R} p_r \geq 1-\alpha$ and is ``abstain'' otherwise.

  The finite loss eliciting $\alpha$ can be written
  $\ell(r,y) = \begin{cases}
  0 & r = y\\
  \alpha & r = \text{abstain}\\
  1 & r \neq y, r \neq \text{abstain}\\
  \end{cases}$.

\cite{ramaswamy2018consistent} show that $\elicpoly(\abstain{1/2}) \leq \ceil{\log_2 n}$, although it is not known if this bound is tight.

>>>>

\begin{definition}[Calibrated Link]\label{def:links}
  Let properties $\gamma:\simplex\toto\R$ and $\Gamma:\simplex\toto\R'$ be given.
  A \emph{link function} is a map $\psi:\R'\to\R$.
  We say that a link $\psi$ is
  \emph{calibrated} if for all $p\in\simplex$, $r'\in \Gamma(p) \implies \psi(r') \in \gamma(p)$; in other words, if for all $r'\in\R'$, $\Gamma_{r'} \subseteq \gamma_{\psi(r')}$.
  It is \emph{separated}, with respect to a loss $L$ eliciting $\Gamma$, if for all $p \in \simplex$,
  \begin{align*}
  \inf_{u \in \R'; \psi(u) \not \in \gamma(p)} \E_{Y\sim p}[L(u, Y)] > \inf_{u \in \R'}\E_{Y\sim p}[L(u, Y)]~.
  \end{align*}
\end{definition}
Roughly speaking, a calibrated link requires that optimal surrogate reports map to optimal original reports, while a separated link adds the stronger guarantee that one cannot approach the optimal surrogate loss while making suboptimal original predictions.
A classic example of a link which is both calibrated and separated is $\psi = \sgn$ when $\gamma=\mode$ and $L$ is either hinge loss or logistic loss.
On the other hand, the link $\psi(u) =-1$ for $u \leq -1$ and $\psi(u) = 1$ for $u > -1$
would not be separated for hinge loss, but it would still be calibrated, as the reports $u\in(-1,1)$ are optimal for hinge loss only when $p=(1/2,1/2)$, in which case both $-1$ and $1$ are optimal for the mode (0-1 loss).
\raft{Aside about other link definitions commented out}
% As a brief aside, it is interesting to contrast the definitions above with the following: a link is
% \emph{exhaustive} if for all $p\in\simplex$, $\gamma(p) = \psi(\Gamma(p)) := \{\psi(r') : r'\in\Gamma(p)\}$.
% A \emph{strong link} is a set-valued function $\psi:\R'\toto\R$ such that for all $p\in\simplex$ and $r'\in\R'$, we have $r'\in\Gamma(p) \implies \gamma(p) = \psi(r')$.
% If sign is interpreted as set-valued (0 maps to $\{1,-1\}$, then it is strong for logistic.  If not, sign is not exhaustive for logistic.  Sign is exhaustive for hinge.}

@@

Often one is given a property $\gamma$ (typically via a discrete loss $\ell$) and one seeks a surrogate loss $L$ with certain attributes, such as convexity, smoothness, etc.
In doing so, we may be interested in the minimum number of dimensions needed for such an indirect elicitation scheme; this is the notion of \emph{elicitation complexity}~\citep{lambert2008eliciting,fissler2016higher,frongillo2015elicitation}.
The two notions of elicitation complexity we use most are as follows: let $\eliccvx(\gamma)$ be the minimum dimension $d$ such that $\gamma$ can be indirectly elicited by a convex loss function $L: \reals^d \to \reals^\Y_+$, and $\elicpoly(\gamma)$ the minimum such $d$ where $L$ is polyhedral.
We will also discuss $\eliccts$, which is the complexity with respect to continuous, real-valued, non-locally-constant properties (\S~\ref{sec:1d}), and $\elicembed$, which is the minimum dimension for $\gamma$ to be embedded (Definition~\ref{def:embedding-dim}).

@@

  A property of interest similar to the mode is the $\abstain{\alpha}$ property.
  In this property in which one reports the most likely outcome if the probability of such an outcome is greater than $1-\alpha$, and otherwise ``abstains'' from reporting.
  That is, $\gamma(p) = \argmax_{r \in \R}p_r$ if $\max_{r \in \R} p_r \geq 1-\alpha$ and is ``abstain'' otherwise.
  The finite loss eliciting $\alpha$ can be written
  $\ell(r,y) = 0$ if $r=y$, $\alpha$ if $r=\text{abstain}$, and $1$ otherwise.
\cite{ramaswamy2018consistent} show that $\elicpoly(\abstain{1/2}) \leq \ceil{\log_2 n}$, although it is not known if this bound is tight.
